\textls[-0]{\thetitle}

### 2023-03-18 cc-condensed.tex
edit

\noindent\YZ{These paragraphs here need to be updated}
Consistency says that the type $\bot$ is not inhabited.
Thus, it is safe to use the type theory for logical reasoning, as not
every proposition is trivially provable.

@@

We prove \cref{thm:consistency} and \cref{thm:canonicity} by constructing a logical-relations model
for the well-formedness rules, following prior approaches~\cite{coquand2018canonicity,sterling2019algebraic,kaposi2019gluing}.

In particular, (1) bottom type is interpreted as an empty set in the model, making sure no syntax derivation of bottom is possible and (2) a closed, well formed type $\goodType{\cdot}{T}{}$ is interpreted
into a logical predicate on closed terms: the predicate includes all
closed, ``reducible'' terms of type~$T$, deriving boolean canonicity.
%\EDJ{I will add a quote around reducible here. it is my bad to introduce "reducible" without defining it first. But my intension is to give a feeling of the dynamic operational semantic for the reader (of course OS is not here in our setting)}\YZreply{Is there a more accurate way to say things here?}\EDJreply{Because in the operational semantic, using ``reducible'' is totally fine. But in declarative style, only ``canonicity'' this word is making sense. But this ``canonicity'' is not friendly to the audience not familar with declartive style.}
% The proof is available as a supplemental file in Agda syntax.
The proof is available in the appendix.

>>>>

\noindent
Consistency says that the type $\bot$ is not inhabited.
Thus, it is safe to use the type theory for logical reasoning, as not
every proposition is trivially provable.

@@

We prove \cref{thm:consistency,thm:canonicity} by constructing a logical-relations model
for the well-formedness rules, following prior approaches~\cite{coquand2018canonicity,kaposi2019gluing,sterling2019algebraic}.
%
The model interprets the bottom type~$\bot$ as an empty set, from which
\cref{thm:consistency} follows.
A closed, well-formed type $\goodType{\cdot}{T}{}$ is interpreted as
a logical predicate on closed terms: the predicate includes all
closed, ``reducible'' terms of type~$T$. So \cref{thm:canonicity} follows.
%\EDJ{I will add a quote around reducible here. it is my bad to introduce "reducible" without defining it first. But my intension is to give a feeling of the dynamic operational semantic for the reader (of course OS is not here in our setting)}\YZreply{Is there a more accurate way to say things here?}\EDJreply{Because in the operational semantic, using ``reducible'' is totally fine. But in declarative style, only ``canonicity'' this word is making sense. But this ``canonicity'' is not friendly to the audience not familar with declartive style.}
% The proof is available as a supplemental file in Agda syntax.
The construction of the logical-relations model is available in
\ifreport
\cref{sec:canonicity-model}.
\else
an appendix.
\fi
